%---------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%---------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Jacob Adley}
\address{421 Westcreek Drive, Warsaw, Indiana 46580}
\address{(574)306-6605 \\ jadley08@gmail.com \\ github.com/jadley08}

\begin{document}

%---------------------------------------------------------
%	EDUCATION SECTION
%---------------------------------------------------------

\begin{rSection}{Education}

{\bf Indiana University, Bloomington} \hfill {\em January 2019 - May 2020} \\
	Computer Science M.S. \hfill { GPA: 4.000 } \\ \\
{\bf Indiana University, Bloomington} \hfill {\em August 2015 - May 2019} \\
Computer Science B.S., Mathematics B.S. \hfill { GPA: 3.764 }
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%---------------------------------------------------------
%    Projects And Seminars
%---------------------------------------------------------
%\begin{rSection}{Projects}
%{\bf Dynamic Analysis of Buckling Restrained Braces}
%\\The project aims at designing and fabrication of two Buckling Restrained Braces which were analyzed under dynamic loading. As alternative for conventional braces, these BRBs are also beneficial for seismic retro-fitting in RCC and steel structures.\\
%\\{\bf Indirect Model Analysis of Structures}\\
%Presented a Seminar on Indirect Model Analysis, explaining the method to compute response of Prototype from the Influence lines obtained from Model. Use of Muller Breslau Principle in Indirect Model Analysis and the Similitude between prototype and  model.\\

%\\{\bf Microtunneling}\\
%Presented a seminar on Micro Tunneling, explaining its advantages over conventional method of drainage laying systems. Analysis considering direct and indirect cost of micro tunneling was also discussed.

%\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
	Programming Languages \ & Racket(Scheme), Java, C, Python, Haskell, Coq, Pie, Javascript \\
	Mathematics & Topology, Real Analysis, Linear Algebra, Calculus \\
	Programming Language Theory \ & Dependent Types, Interpreters, Custom Languages, Compilers \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

	\begin{rSubsection}{Service Now}{May 2019 - August 2019}{Platform Engineering Intern}{}
		\item Created a new UI feature to dynamically render titles based on user values relying on full stack production.
		\item Worked to alter the core database functionality to decrease the number of records needed per customer instance.
	\end{rSubsection}

	\begin{rSubsection}{Crowe LLP}{May 2018 - August 2018}{Applied Technology Intern}{}
		\item Worked as sole web engineer on team, requiring new UI pages and middle layer solutions done in C\#.
		\item Coordinated with database team members on all projects to ensure maximal efficiency when working with terrabytes of data.
	\end{rSubsection}

	\begin{rSubsection}{Indiana University SICE Department}{August 2017 - December 2017}{Undergraduate Instructor: Fundamentals of Data Structures}{}
		\item Helped dynamically develop a curriculum based on student performance and overall feedback.
		\item Responsible for running lab sections, holding office hours, grading and preparing all assignments and examinations.
	\end{rSubsection}

\end{rSection}

%---------------------------------------------------------
% Extra Curricular
%---------------------------------------------------------
\begin{rSection}{Extra-Curricular} \itemsep -3pt
	\item Club Runner - Compete in distances from 8K to Marathon.
	\item Karate Club - Athlete and Club Treasurer. Responsible for organization of all financial aspects.
	\item Linux - Interested in customizing operating systems (Arch) and software (Vim, Suckless Utilities) to their fullest extent.
	\item Intermediate chess student, intermediate violin student, avid reader.
\end{rSection}

\end{document}
